---
title: "04_Tolerances-and-Traits"
output: html_document
date: "2023-02-16"
---


#epi and meso ranges

```{r replot epi and meso tolerance as violin plots}
# vs temp range
testres_ph <- dunnTest(temprange ~ classification,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(19)
epimesotemp <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = temprange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 21, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesotemp

testres_ph <- dunnTest(fluorrange ~ classification,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.4)
epimesofluor <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")  + 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  ggtitle("Chl-a range")+ 
  xlab(NULL) + 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.6, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesofluor

testres_ph <- dunnTest(oxyrange ~ classification,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300)
epimesooxy <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")  + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen")+ 
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 325, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesooxy

strata_provinces <- ggplot(alltaxaranges, aes(x = classification, y = nstations, group = classification)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  ylab("Provinces (N)") + 
  xlab(NULL) + 
  # theme(text = element_text(size = 9),
  #       plot.title = element_text(size = 10))   +
  stat_compare_means(method = "kruskal.test", method.args= list(alternative = "two.sided"), label.y = 3.4, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
ylim(0.5,3.6)


# epimesosal <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = salrange)) + 
#   geom_jitter(width = 0.3) +
#   geom_violin(alpha=0.3) +
#     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
#   ylab("Salinity range") + 
#   xlab(NULL) + 
#   ggtitle("Stratum")+ 
#   geom_hline(yintercept = mean(alltaxaranges$temprange), linetype = 2)+ # Add horizontal line at base mean
#   stat_compare_means(method = "wilcox.test", label.y = 2.25)+        # Add global annova p-value
#   stat_compare_means(label = "p.signif", method = "t.test",
#                      ref.group = ".all.", label.y = 2)   
# 
# 

plots <- ggarrange(epimesotemp + ylim(0,23) + ggtitle("Temperature range"), epimesofluor + ylim(0,2.8) + ggtitle("Chl-a range") +
                     theme(plot.title = element_markdown()) , epimesooxy + ylim(0,350) + ggtitle("Oxygen range"),  ncol = 3, nrow = 1, align = "hv", labels = "auto")

pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/Epi_Meso_EnviroRanges.pdf", height =3, width = 6.5)
plots
dev.off()


jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/Epi_Meso_EnviroRanges.jpeg", height =3, width = 6.5, unit = "in", quality = 100, res = 300 )
plots
dev.off()
```



## environmental range and number of stations of epi and meso


```{r epi and meso}
#taxawithatleast10 <- names(table(alltaxaranges$Class))[table(alltaxaranges$Class) > 10]
#together_taxtable_atleast10 <- alltaxaranges[alltaxaranges$Class %in% taxawithatleast10,]
#together_taxtable_atleast10 <- together_taxtable_atleast10[together_taxtable_atleast10$Class == "Hexanauplia",]
#taxawithatleast10 <- names(table(together_taxtable_atleast10$Family))[table(together_taxtable_atleast10$Family) > 10]
#together_taxtable_atleast10 <- together_taxtable_atleast10[together_taxtable_atleast10$Family %in% taxawithatleast10,]
alltaxaranges$nstations_fac <- as.factor(alltaxaranges$nstations)

testres <- kruskal.test(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(oxyrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(oxyrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(fluorrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(fluorrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(salrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(salrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]

## 

testres <- kruskal.test(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(oxyrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(oxyrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(fluorrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(fluorrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(salrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,])
testres
testres_ph <- dunnTest(salrange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" & alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]

##plots
# vs temp range
testres_ph <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(19, 21)
stationstemp_epi <- ggplot(alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = temprange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature, Epipelagic")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 23,
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationstemp_epi

testres_ph <- dunnTest(fluorrange ~ nstations_fac,
                       data=alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.5, 2.7)
stationsfluor_epi <- ggplot(alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  xlab(NULL) + 
  ggtitle("Chl-a, Epipelagic")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.9, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationsfluor_epi

testres_ph <- dunnTest(oxyrange ~ nstations_fac,
                       data=alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300, 325)
stationsoxy_epi <- ggplot(alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen, Epipelagic")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 350, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationsoxy_epi

testres_ph <- dunnTest(salrange ~ nstations_fac,
                       data=alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.1, 2.3)
stationssal_epi <- ggplot(alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = salrange)) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  ylab("Range") +
  xlab(NULL) +
  ggtitle("Salinity, Epipelagic")+
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.5, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationssal_epi

####### 

testres_ph <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
#nsamples_posthoc$ypos <- c(19)
stationstemp_meso <- ggplot(alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = temprange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature, Mesopelagic")+ 
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 19,
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationstemp_meso

testres_ph <- dunnTest(fluorrange ~ nstations_fac,
                       data=alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.5)
stationsfluor_meso <- ggplot(alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  xlab(NULL) + 
  ggtitle("Chl-a, Mesopelagic")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.7, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationsfluor_meso

testres_ph <- dunnTest(oxyrange ~ nstations_fac,
                       data=alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300, 325)
stationsoxy_meso <- ggplot(alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen, Mesopelagic")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 350,  
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationsoxy_meso

testres_ph <- dunnTest(salrange ~ nstations_fac,
                       data=alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.1, 2.3)
stationssal_meso <- ggplot(alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = salrange)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) +
  ylab("Range") +
  xlab(NULL) +
  ggtitle("Salinity, Mesopelagic")+
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.5,  
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
stationssal_meso




epiplots <- ggarrange(stationstemp_epi + ylim(0,23), stationsfluor_epi + ylim(0,3.1), stationsoxy_epi + ylim(0,370), stationssal_epi + ylim(0,2.8), ncol = 4, nrow = 1, align = "hv", labels = "auto")
plots <- annotate_figure(plots, bottom = text_grob("Provinces (N)"))

mesoplots <- ggarrange(stationstemp_meso+ ylim(0,23), stationsfluor_meso + ylim(0,3.1), stationsoxy_meso + ylim(0,370), stationssal_meso + ylim(0,2.8), ncol = 4, nrow = 1, align = "hv", labels = "auto")
plots <- annotate_figure(plots, bottom = text_grob("Provinces (N)"))

epiandmesoplots <- ggarrange(stationstemp_epi + ylim(0,23), stationsfluor_epi + ylim(0,3.1), stationsoxy_epi + ylim(0,370), stationssal_epi + ylim(0,2.8),stationstemp_meso + ylim(0,23), stationsfluor_meso + ylim(0,3.1), stationsoxy_meso + ylim(0,370), stationssal_meso + ylim(0,2.8), ncol = 4, nrow = 2, align = "hv", labels = "auto")
epiandmesoplots <- annotate_figure(epiandmesoplots, bottom = text_grob("Provinces (N)"))
epiandmesoplots

epiandmesoplots3 <- ggarrange(stationstemp_epi + ylim(0,24), stationsfluor_epi + ylim(0,3.1), stationsoxy_epi + ylim(0,370), stationstemp_meso + ylim(0,21), stationsfluor_meso + ylim(0,3), stationsoxy_meso + ylim(0,370), ncol = 3, nrow = 2, align = "hv", labels = "auto")
epiandmesoplots3 <- annotate_figure(epiandmesoplots3, bottom = text_grob("Provinces (N)"))
epiandmesoplots3

epiandmesowithsharedlables <- ggarrange(stationstemp_epi + ylim(0,24) + ggtitle(NULL), 
                                        stationsfluor_epi + ylim(0,3.1)+ ggtitle(NULL), 
                                        stationsoxy_epi + ylim(0,370)+ ggtitle(NULL), 
                                        stationstemp_meso + ylim(0,21)+ ggtitle(NULL), 
                                        stationsfluor_meso + ylim(0,3)+ ggtitle(NULL), 
                                        stationsoxy_meso + ylim(0,370)+ ggtitle(NULL), 
                                        ncol = 3, nrow = 2, align = "hv", labels = "auto")
epiandmesowithsharedlables <- annotate_figure(epiandmesowithsharedlables, left = text_grob("  Mesopelagic                            Epipelagic", rot = 90))


epiandmesowithsharedlables <- annotate_figure(epiandmesowithsharedlables, top = text_grob("                  Temperature                              Chl-a                                 Oxygen        "))

epiandmesowithsharedlables


pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/EpiMesoNstations.pdf", height =4.5, width = 6.5)
epiandmesowithsharedlables
dev.off()
jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/EpiMesoNstations.jpeg", height =4.5, width = 6.5, unit = "in", quality = 100, res = 300 )
epiandmesowithsharedlables
dev.off()


pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/epiandmeso_nstations_observedenviroranges_sig.pdf", height =6.5, width = 10)
epiandmesoplots
dev.off()
jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/epiandmeso_nstations_observedenviroranges_sig.jpeg", height =6.5, width = 10, unit = "in", quality = 100, res = 300 )
epiandmesoplots
dev.off()


pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/epiandmeso_nstations_observedenviroranges_nosal.pdf", height =6.2, width = 8.5)
epiandmesoplots3
dev.off()
jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/epiandmeso_nstations_observedenviroranges_nosal.jpeg", height =6.2, width = 8.5, unit = "in", quality = 100, res = 300 )
epiandmesoplots3
dev.off()

```


##epi and meso ranges subset by N


```{r}


##plots
# vs temp range
# testres_ph <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,],
#                        method="bonferroni")
# nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
# nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
# nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
# nsamples_posthoc$P.adj.sig <- NA
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
# nsamples_posthoc$ypos <- c(19, 21)
stationstemp_epiandmeso <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = temprange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black", 
               size = 2,
               alpha = 0.7) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 25.5,
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns")))  + 
  geom_pwc(method = "dunn.test",
           label = "p.adj.signif", 
           hide.ns = T, 
           symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns")),
           tip.length = 0.01,
           bracket.nudge.y = 0.04,
           vjust = 0.5) +
  facet_wrap(.~classification)+ 
  theme(strip.background = element_rect(fill="white"), 
        strip.text.x = element_text(size = 8),
        plot.title = element_text(size = 11))
stationstemp_epiandmeso



# testres_ph <- dunnTest(fluorrange ~ nstations_fac,
#                        data=alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,],
#                        method="bonferroni")
# nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
# nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
# nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
# nsamples_posthoc$P.adj.sig <- NA
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
# nsamples_posthoc$ypos <- c(2.5, 2.7)
stationsfluor_epiandmeso <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black", 
               size = 2,
               alpha = 0.7) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown())+
  xlab(NULL) + 
  ggtitle("Chl-a")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 3.13, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) +
  
  geom_pwc(method = "dunn.test",
           label = "p.adj.signif", 
           hide.ns = T, 
           symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns")),
           tip.length = 0.01,
           bracket.nudge.y = 0.04,
           vjust = 0.5) +
  facet_wrap(.~classification)+ 
  theme(strip.background = element_rect(fill="white"), 
        strip.text.x = element_text(size = 8),
        plot.title = element_text(size = 11))
stationsfluor_epiandmeso




# testres_ph <- dunnTest(oxyrange ~ nstations_fac,
#                        data=alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,],
#                        method="bonferroni")
# nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
# nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
# nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
# nsamples_posthoc$P.adj.sig <- NA
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
# nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
# nsamples_posthoc$ypos <- c(300, 325)
stationsoxy_epiandmeso <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = nstations_fac, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black", 
               size = 2,
               alpha = 0.7) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5)) + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 370, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) + 
  geom_pwc(method = "dunn.test",
           label = "p.adj.signif", 
           hide.ns = T, 
           symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns")),
           tip.length = 0.01,
           bracket.nudge.y = 0.04,
           vjust = 0.5) +
  facet_wrap(.~classification)+ 
  theme(strip.background = element_rect(fill="white"), 
        strip.text.x = element_text(size = 8),
        plot.title = element_text(size = 11))
stationsoxy_epiandmeso



####### 


epiandmesoplotsfacet3 <- ggarrange(stationstemp_epiandmeso + ylim(0,26.5), 
                                   stationsfluor_epiandmeso + ylim(0,3.3), 
                                   stationsoxy_epiandmeso + ylim(0,390), 
                                   ncol = 3, nrow = 1, align = "hv", labels = "auto")

epiandmesoplotsfacet3 <- annotate_figure(epiandmesoplotsfacet3, bottom = text_grob("Provinces (N)"))


epiandmesoplotsfacet3



pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/NStationsEnvRangeEpiMesoFacet.pdf", height =3, width = 6.5)
epiandmesoplotsfacet3
dev.off()
jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/NStationsEnvRangeEpiMesoFacet.jpeg", height =3, width = 6.5, unit = "in", quality = 100, res = 300 )
epiandmesoplotsfacet3
dev.off()


```





```{r grouped violin}
# vs temp range
testres_epiwithin <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Epipelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                              method="bonferroni")
nsamples_posthocepi <- testres_epiwithin$res[testres_epiwithin$res$P.adj < 0.05,]
nsamples_posthocepi$group1 <- sapply(strsplit(nsamples_posthocepi$Comparison, " - "), '[', 1)
nsamples_posthocepi$group2 <- sapply(strsplit(nsamples_posthocepi$Comparison, " - "), '[', 2)
nsamples_posthocepi$P.adj.sig <- NA
nsamples_posthocepi$P.adj.sig[nsamples_posthocepi$P.adj < 0.05] <- "*"
nsamples_posthocepi$P.adj.sig[nsamples_posthocepi$P.adj < 0.01] <- "**"
nsamples_posthocepi$P.adj.sig[nsamples_posthocepi$P.adj < 0.001] <- "***"
nsamples_posthocepi$ypos <- c(19, 21)

testres_mesowithin <- dunnTest(temprange ~ nstations_fac, alltaxaranges[alltaxaranges$classification == "Mesopelagic" &alltaxaranges$taxa_nsamplestotal > 1,],
                               method="bonferroni")
nsamples_posthocmeso <- testres_mesowithin$res[testres_mesowithin$res$P.adj < 0.05,]
nsamples_posthocmeso$group1 <- sapply(strsplit(nsamples_posthocmeso$Comparison, " - "), '[', 1)
nsamples_posthocmeso$group2 <- sapply(strsplit(nsamples_posthocmeso$Comparison, " - "), '[', 2)
nsamples_posthocmeso$P.adj.sig <- NA
nsamples_posthocmeso$P.adj.sig[nsamples_posthocmeso$P.adj < 0.05] <- "*"
nsamples_posthocmeso$P.adj.sig[nsamples_posthocmeso$P.adj < 0.01] <- "**"
nsamples_posthocmeso$P.adj.sig[nsamples_posthocmeso$P.adj < 0.001] <- "***"
nsamples_posthocmeso$ypos <- c(19, 21)

epimesotempnstations <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = temprange, fill = nstations_fac)) + 
  geom_point(position=position_jitterdodge(dodge.width = 0.8), aes(group = nstations_fac), alpha = 0.4, size = 0.5) +
  #geom_jitter( alpha = 0.4, size = 0.5, position = "dodge") +
  geom_violin(alpha=0.3, position=position_dodge(width=0.8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black",
               position = position_dodge(width = 0.8)) + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature")+ 
  stat_compare_means(method = "kruskal.test", label.y = 20, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) +
  stat_compare_means(mapping = aes(x = classification, y = temprange), 
                     inherit.aes = FALSE,
                     method = "kruskal.test", label.y = 22, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) + 
  geom_bracket(data = alltaxaranges, aes(x = classification, y = temprange), xmin = "Epipelagic", xmax = "Mesopelagic", y.position = 22, label = "") + 
  scale_fill_manual(values = c("white", "white", "white")) 
  
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  
  epimesotempnstations

testres_ph <- dunnTest(fluorrange ~ classification,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.4)
epimesofluor <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")  + 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  ggtitle("Chl-a range")+ 
  xlab(NULL) + 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.6, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesofluor

testres_ph <- dunnTest(oxyrange ~ classification,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300)
epimesooxy <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")  + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen")+ 
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 325, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesooxy

strata_provinces <- ggplot(alltaxaranges, aes(x = classification, y = nstations, group = classification)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  ylab("Provinces (N)") + 
  xlab(NULL) + 
  # theme(text = element_text(size = 9),
  #       plot.title = element_text(size = 10))   +
  stat_compare_means(method = "kruskal.test", method.args= list(alternative = "two.sided"), label.y = 3.4, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
ylim(0.5,3.6)


# epimesosal <- ggplot(alltaxaranges[alltaxaranges$taxa_nsamplestotal > 1,], aes(x = classification, y = salrange)) + 
#   geom_jitter(width = 0.3) +
#   geom_violin(alpha=0.3) +
#     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
#   ylab("Salinity range") + 
#   xlab(NULL) + 
#   ggtitle("Stratum")+ 
#   geom_hline(yintercept = mean(alltaxaranges$temprange), linetype = 2)+ # Add horizontal line at base mean
#   stat_compare_means(method = "wilcox.test", label.y = 2.25)+        # Add global annova p-value
#   stat_compare_means(label = "p.signif", method = "t.test",
#                      ref.group = ".all.", label.y = 2)   
# 
# 

plots <- ggarrange(epimesotemp + ylim(0,23) + ggtitle("Temperature range"), epimesofluor + ylim(0,2.8) + ggtitle("Chl-a range") +
                     theme(plot.title = element_markdown()) , epimesooxy + ylim(0,350) + ggtitle("Oxygen range"),  ncol = 3, nrow = 1, align = "hv", labels = "auto")

pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/Epi_Meso_EnviroRanges.pdf", height =3, width = 6.5)
plots
dev.off()


jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/Epi_Meso_EnviroRanges.jpeg", height =3, width = 6.5, unit = "in", quality = 100, res = 300 )
plots
dev.off()
```








are there traits that are associated with greater environmental tolerance, or greater # of nets? 

```{r epi and meso tolerances among trait states}
testdataframe <- alltaxaranges[alltaxaranges$classification == "Epipelagic",c("temprange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
temprangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$temprange ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Epipelagic",c("fluorrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
fluorrangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$fluorrange ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Epipelagic",c("oxyrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
oxyrangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$oxyrange ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Epipelagic",c("salrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
salrangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$salrange ~ x))

epipvals <- sapply(temprangeres, "[[", 3)  
epipvals <- rbind(epipvals, sapply(fluorrangeres, "[[", 3) )
epipvals <- rbind(epipvals, sapply(oxyrangeres, "[[", 3) )
epipvals <- rbind(epipvals, sapply(salrangeres, "[[", 3) )
rownames(epipvals) <- c("EpiTemp", "EpiFluor", "EpiOxy", "EpiSal")


testdataframe <- alltaxaranges[alltaxaranges$classification == "Mesopelagic",c("temprange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
temprangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$temprange ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Mesopelagic",c("fluorrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
fluorrangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$fluorrange ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Mesopelagic",c("oxyrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
oxyrangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$oxyrange ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Mesopelagic",c("salrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
salrangeres <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$salrange ~ x))

mesopvals <- sapply(temprangeres, "[[", 3)  
mesopvals <- rbind(mesopvals, sapply(fluorrangeres, "[[", 3) )
mesopvals <- rbind(mesopvals, sapply(oxyrangeres, "[[", 3) )
mesopvals <- rbind(mesopvals, sapply(salrangeres, "[[", 3) )
rownames(mesopvals) <- c("MesoTemp", "MesoFluor", "MesoOxy", "MesoSal")


epipvals
epipvals < 0.05

mesopvals
mesopvals < 0.05



testdataframe <- alltaxaranges[,c("temprange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
temprangeres_all <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$temprange ~ x))

testdataframe <- alltaxaranges[,c("fluorrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
fluorrangeres_all <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$fluorrange ~ x))

testdataframe <- alltaxaranges[,c("oxyrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
oxyrangeres_all <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$oxyrange ~ x))

testdataframe <- alltaxaranges[,c("salrange", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
salrangeres_all <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$salrange ~ x))

allpvals <- sapply(temprangeres_all, "[[", 3)  
allpvals <- rbind(allpvals, sapply(fluorrangeres_all, "[[", 3) )
allpvals <- rbind(allpvals, sapply(oxyrangeres_all, "[[", 3) )
allpvals <- rbind(allpvals, sapply(salrangeres_all, "[[", 3) )
rownames(allpvals) <- c("Temp", "Fluor", "Oxy", "Sal")


allpvals
allpvals < 0.05




```


within epi and meso, are there traits that are associated with larger spatial extent?  (i.e. dvm > more stations)
```{r}
testdataframe <- alltaxaranges[alltaxaranges$classification == "Epipelagic",c("nstations", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
stationsrangeres_epi <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$nstations ~ x))

testdataframe <- alltaxaranges[alltaxaranges$classification == "Mesopelagic",c("nstations", "Diet", "FeedingBehavior", "Spawning", "AsexualRepro", "Carbon", "anymigration")]
stationsrangeres_meso <- lapply(testdataframe[-1], function(x) kruskal.test(testdataframe$nstations ~ x))

pvalstraitsnum_epi <- sapply(stationsrangeres_epi, "[[", 3)  
pvalstraitsnum_meso <- sapply(stationsrangeres_meso, "[[", 3)  
pvalstraitsnum <- rbind(pvalstraitsnum_epi, pvalstraitsnum_meso )
rownames(pvalstraitsnum) <- c("Epi", "Meso")
pvalstraitsnum
pvalstraitsnum < 0.05

```


#Epipelagic: 
asex repro on fluor; provinces
carbon on provinces;


#Mesopelagic: 
diet on fluor, oxy; 
feeding behavior on oxy; provinces


#Total: 
migration on all three enviro; provinces 


#plot significant traits:

epi: asex repro on fluor; provinces
```{r plot epipelagic asexual repro}
#asexual vs fluor range
testres_ph <- dunnTest(fluorrange ~ AsexualRepro,
                       data=alltaxaranges[alltaxaranges$classification == "Epipelagic" & !is.na(alltaxaranges$AsexualRepro),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.4)
epi_asex_fluor <- ggplot(alltaxaranges[alltaxaranges$classification == "Epipelagic"& !is.na(alltaxaranges$AsexualRepro),], aes(x = AsexualRepro, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  # scale_y_log10()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  xlab("Asexual reproduction") + 
  ggtitle("Chl-a range")+ 
  ylim(0,3)+
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.5, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epi_asex_fluor


#asexual vs provinces
testres_ph <- dunnTest(nstations ~ AsexualRepro,
                       data=alltaxaranges[!is.na(alltaxaranges$AsexualRepro) & alltaxaranges$classification == "Epipelagic",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(3.3)

epi_asex_provinces <- ggplot(alltaxaranges[!is.na(alltaxaranges$AsexualRepro) & alltaxaranges$classification == "Epipelagic",], aes(x = AsexualRepro, y = nstations, group = AsexualRepro)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab("Provinces (N)") + 
  xlab("Asexual reproduction") + 
  ylim(1,4.1) + 
  ggtitle("Distributional range")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 3.6, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epi_asex_provinces
```

epi: carbon on provinces;
```{r plot epipelagic carbon}
#carbon vs provinces
testres_ph <- dunnTest(nstations ~ Carbon,
                       data=alltaxaranges[!is.na(alltaxaranges$Carbon) & alltaxaranges$classification == "Epipelagic",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(3.3, 3.6)

epi_carbon_provinces <- ggplot(alltaxaranges[!is.na(alltaxaranges$Carbon) & alltaxaranges$classification == "Epipelagic",], aes(x = Carbon, y = nstations, group = Carbon)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab("Provinces (N)") + 
  xlab("Body carbon composition") + 
  ylim(1,4.1)+
  ggtitle("Distributional range")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 3.9, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epi_carbon_provinces
```


meso: diet on fluor, oxy; 
```{r}
#diet vs oxy range
testres_ph <- dunnTest(oxyrange ~ Diet,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet) & alltaxaranges$classification == "Mesopelagic",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]
meso_diet_oxy <- ggplot(alltaxaranges[!is.na(alltaxaranges$Diet) & alltaxaranges$classification == "Mesopelagic",], aes(x = Diet, y = oxyrange)) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Range<br>(\U003BCmol kg<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  xlab("Diet") +
  ylim(0,340) +
  ggtitle("Oxygen<br>range")+
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 310, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
meso_diet_oxy


#diet vs fluor range
testres_ph <- dunnTest(fluorrange ~ Diet,
                       data=alltaxaranges[!is.na(alltaxaranges$Diet) & alltaxaranges$classification == "Mesopelagic",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.4)
meso_diet_fluor <- ggplot(alltaxaranges[!is.na(alltaxaranges$Diet) & alltaxaranges$classification == "Mesopelagic",], aes(x = Diet, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  # scale_y_log10()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_markdown()) + 
  ylab("Range<br>(\U003BCg L<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  xlab("Diet") + 
  ggtitle("Chl-a<br>range")+ 
  ylim(0,2.8) +
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.5, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
meso_diet_fluor


```


meso: feeding behavior on oxy; provinces
```{r}
#feeding vs oxy range
testres_ph <- dunnTest(oxyrange ~ FeedingBehavior,
                       data=alltaxaranges[!is.na(alltaxaranges$FeedingBehavior) & alltaxaranges$classification == "Mesopelagic",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]
meso_feeding_oxy <- ggplot(alltaxaranges[!is.na(alltaxaranges$FeedingBehavior) & alltaxaranges$classification == "Mesopelagic",], aes(x = FeedingBehavior, y = oxyrange)) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Range<br>(\U003BCmol kg<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown(),
        axis.title.x = element_markdown())+ 
  xlab("Feeding<br>strategy") +
  ylim(0,340) + 
  ggtitle("Oxygen<br>range")+
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 310, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
meso_feeding_oxy


#feeding vs provinces
testres_ph <- dunnTest(nstations ~ FeedingBehavior,
                       data=alltaxaranges[!is.na(alltaxaranges$FeedingBehavior) & alltaxaranges$classification == "Mesopelagic",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(3.3, 3.6)

meso_feeding_provinces <- ggplot(alltaxaranges[!is.na(alltaxaranges$FeedingBehavior) & alltaxaranges$classification == "Mesopelagic",], aes(x = FeedingBehavior, y = nstations, group = FeedingBehavior)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_markdown(),
        axis.title.x = element_markdown()) + 
  ylab("Provinces (N)") + 
  xlab("Feeding<br>strategy") + 
  ylim(1,4.1) + 
  ggtitle("Distributional<br>range")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 3.9, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
meso_feeding_provinces


```



overall: migration on all enviro; provinces
```{r}
#dvm vs range of temp
testres_ph <- dunnTest(temprange ~ anymigration,
                       data=alltaxaranges[!is.na(alltaxaranges$anymigration),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(20)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]
total_mig_temp <- ggplot(alltaxaranges[!is.na(alltaxaranges$anymigration),], aes(x = anymigration, y = temprange)) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") +
  ylab("Range<br>(\u00B0C)") + 
  xlab("DVM") +
  scale_x_discrete(labels=c("Yes", "No")) +
  ylim(0,24) + 
  ggtitle("Temperature<br>range")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_markdown(),
        plot.title = element_markdown()) +
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 22, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
total_mig_temp

#dvm vs oxy range
testres_ph <- dunnTest(oxyrange ~ anymigration,
                       data=alltaxaranges[!is.na(alltaxaranges$anymigration),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]
total_mig_oxy <- ggplot(alltaxaranges[!is.na(alltaxaranges$anymigration),], aes(x = anymigration, y = oxyrange)) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Range<br>(\U003BCmol kg<sup>-1</sup>)")+
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  xlab("DVM") +
  scale_x_discrete(labels=c("Yes", "No")) +
  ylim(0,340) + 
  ggtitle("Oxygen<br>range")+
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 320, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
total_mig_oxy


#dvm vs fluor range
testres_ph <- dunnTest(fluorrange ~ anymigration,
                       data=alltaxaranges[!is.na(alltaxaranges$anymigration),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.4)
total_mig_fluor <- ggplot(alltaxaranges[!is.na(alltaxaranges$anymigration),], aes(x = anymigration, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  # scale_y_log10()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  ylab("Range<br>(\U003BCg L<sup>-1</sup>)")+
  xlab("DVM") +
  scale_x_discrete(labels=c("Yes", "No")) +
  ylim(0,2.8) + 
  labs(title = "Chl-a <br>range")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.6, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
total_mig_fluor



#dvm vs provinces
testres_ph <- dunnTest(nstations ~ anymigration,
                       data=alltaxaranges[!is.na(alltaxaranges$anymigration),],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(3.3)

total_mig_provinces <- ggplot(alltaxaranges[!is.na(alltaxaranges$anymigration),], aes(x = anymigration, y = nstations, group = anymigration)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_markdown()) + 
  ylab("Provinces (N)") + 
  xlab("DVM") +
  scale_x_discrete(labels=c("Yes", "No")) +
  ylim(1,3.7) + 
  ggtitle("Distributional<br>range")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 3.6, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
total_mig_provinces



```


```{r plot epipelagic}
plots_epi <- ggarrange(epi_asex_fluor, epi_asex_provinces, epi_carbon_provinces,
                       nrow = 1, ncol = 3, align = "hv", labels = "auto")
plots_epi

pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/epipelagic_traits_ranges.pdf", height =3, width = 6.5)
plots_epi
dev.off()

jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/epipelagic_traits_ranges.jpeg", height =3, width = 6.5, unit = "in", quality = 100, res = 300)
plots_epi
dev.off()
```


```{r plot mesopelagic}
plots_meso <- ggarrange(meso_diet_fluor, meso_diet_oxy, meso_feeding_oxy, meso_feeding_provinces,
                        nrow = 1, ncol = 4, align = "hv", labels = "auto")
plots_meso


pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/mesopelagic_traits_ranges.pdf", height =4, width = 7)
plots_meso
dev.off()

jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/mesopelagic_traits_ranges.jpeg", height =4, width = 7, unit = "in", quality = 100, res = 300)
plots_meso
dev.off()
```


```{r plot migration}
plots_mig <- ggarrange(total_mig_temp, total_mig_fluor, total_mig_oxy, total_mig_provinces,
                       nrow = 1, ncol = 4, align = "hv", labels = "auto")
plots_mig

pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/migration_traits_ranges.pdf", height =4, width = 7)
plots_mig
dev.off()

jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/migration_traits_ranges.jpeg", height =4, width = 7, unit = "in", quality = 100, res = 300)
plots_mig
dev.off()

```




## Are there taxonomic groups that are more/less likely to be found in multiple stations or provinces?

Which taxonomic groups are shared or different among provinces? 
Are there taxa that are more/less likely to be found in multiple provinces?
```{r}

taxawithatleast10 <- names(table(alltaxaranges$Class))[table(alltaxaranges$Class) > 10]
together_taxtable_atleast10 <- alltaxaranges[alltaxaranges$Class %in% taxawithatleast10,]
together_taxtable_atleast10$Class[together_taxtable_atleast10$Class == "Hexanauplia"] <- "Copepoda"



testres <- kruskal.test(taxa_nsamplestotal ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(taxa_nsamplestotal ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph

testres <- kruskal.test(nstations ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(nstations ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph
##plots

testres_ph <- dunnTest(taxa_nsamplestotal ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(50,53,56)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]
classsamples <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class != "",], aes(x = Class, y = taxa_nsamplestotal, group = Class)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.6)  +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Samples (N)") +
  xlab(NULL) +
  ggtitle("Taxa occurring in multiple samples") +
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 60, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 

classsamples


testres_ph <- dunnTest(nstations ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(3.3,3.6)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]
classprovinces <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class != "",], aes(x = Class, y = nstations, group = Class)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.6)  +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Provinces (N)") +
  xlab(NULL) +
  ggtitle("Taxonomic Class")+
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 3.9,
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) +
  ylim(0.5,4.1)
classprovinces

taxawithatleast10 <- names(table(alltaxaranges$Family))[table(alltaxaranges$Family) > 10]
testres <- kruskal.test(taxa_nsamplestotal ~ Family, together_taxtable_atleast10[together_taxtable_atleast10$Class == "Copepoda" & 
                                                                                   together_taxtable_atleast10$Family != "" &
                                                                                   together_taxtable_atleast10$Family %in% taxawithatleast10,])
testres
testres <- kruskal.test(nstations ~ Family, together_taxtable_atleast10[together_taxtable_atleast10$Class == "Copepoda" & 
                                                                          together_taxtable_atleast10$Family != "" &
                                                                          together_taxtable_atleast10$Family %in% taxawithatleast10,])
testres



testres_ph <- dunnTest(nstations ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class == "Copepoda" & 
                                                          together_taxtable_atleast10$Family != "" &
                                                          together_taxtable_atleast10$Family %in% taxawithatleast10,],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(3.3, 3.6, 3.9)
nsamples_posthoc <- nsamples_posthoc[,c("group1", "group2", "P.adj", "P.adj.sig", "ypos")]

copepodprovinces <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class == "Copepoda" & 
                                                         together_taxtable_atleast10$Family != "" &
                                                         together_taxtable_atleast10$Family %in% taxawithatleast10,], 
                           aes(x = Family, 
                               y = nstations, 
                               group = Family)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.6)  +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Provinces (N)") +
  xlab(NULL) +
  ggtitle("Copepod Families")+
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 4.2, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) +
  ylim(0.5,4.5)
copepodprovinces


plots <- ggarrange(classprovinces, copepodprovinces, nrow = 2, ncol = 1, align = "hv", labels = "auto")
plots

pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/taxonomy_num_stations.pdf", height =6, width = 3)
plots
dev.off()

jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/taxonomy_num_stations.jpeg", height =6, width = 3, unit = "in", quality = 100, res = 300)
plots
dev.off()


```


## supplemental: ranges of taxa
## differences in environmental range among taxonomic groups

```{r tolerance between classes, families}

taxawithatleast10 <- names(table(alltaxaranges$Class))[table(alltaxaranges$Class) > 10]
together_taxtable_atleast10 <- alltaxaranges[alltaxaranges$Class %in% taxawithatleast10,]
together_taxtable_atleast10$Class[together_taxtable_atleast10$Class == "Hexanauplia"] <- "Copepoda"

testres <- kruskal.test(temprange ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(temprange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph

testres <- kruskal.test(oxyrange ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(oxyrange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph

testres <- kruskal.test(fluorrange ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(fluorrange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph

testres <- kruskal.test(salrange ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(salrange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph

testres <- kruskal.test(nstations ~ Class, together_taxtable_atleast10[together_taxtable_atleast10$Class != "",])
testres
testres_ph <- dunnTest(nstations ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
testres_ph
##plots
# vs temp range
testres_ph <- dunnTest(temprange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(19, 21)
epimesotemp <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class != "",], aes(x = Class, y = temprange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 23, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesotemp

testres_ph <- dunnTest(fluorrange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
#nsamples_posthoc$ypos <- c(2.4)
epimesofluor <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class != "",], aes(x = Class, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab("Range (mg m<sup>-3</sup>)")+
  theme(axis.title.y = element_markdown())+ 
  xlab(NULL) + 
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  ggtitle("Chl-a")+ 
  #  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.6,
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesofluor

testres_ph <- dunnTest(oxyrange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
#nsamples_posthoc$ypos <- c(300)
epimesooxy <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class != "",], aes(x = Class, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen")+ 
  #stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 325, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesooxy

testres_ph <- dunnTest(salrange ~ Class,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Class != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
#nsamples_posthoc$ypos <- c(300)
epimesosal <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Class != "",], aes(x = Class, y = salrange)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Range") +
  xlab(NULL) +
  ggtitle("Salinity")+
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.1, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 



plots_classes <- ggarrange(epimesotemp + ylim(0,25), epimesofluor + ylim(0,2.8), epimesooxy + ylim(0,350), ncol = 3, nrow = 1, align = "hv", labels = "auto")


```

```{r tolerance between copepod families}

taxawithatleast10 <- names(table(alltaxaranges$Class))[table(alltaxaranges$Class) > 10]
together_taxtable_atleast10 <- alltaxaranges[alltaxaranges$Class %in% taxawithatleast10,]
together_taxtable_atleast10 <- together_taxtable_atleast10[together_taxtable_atleast10$Class == "Hexanauplia",]
taxawithatleast10 <- names(table(together_taxtable_atleast10$Family))[table(together_taxtable_atleast10$Family) > 10]
together_taxtable_atleast10 <- together_taxtable_atleast10[together_taxtable_atleast10$Family %in% taxawithatleast10,]

testres <- kruskal.test(temprange ~ Family, together_taxtable_atleast10[together_taxtable_atleast10$Family != "",])
testres
testres_ph <- dunnTest(temprange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(oxyrange ~ Family, together_taxtable_atleast10[together_taxtable_atleast10$Family != "",])
testres
testres_ph <- dunnTest(oxyrange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(fluorrange ~ Family, together_taxtable_atleast10[together_taxtable_atleast10$Family != "",])
testres
testres_ph <- dunnTest(fluorrange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]


testres <- kruskal.test(salrange ~ Family, together_taxtable_atleast10[together_taxtable_atleast10$Family != "",])
testres
testres_ph <- dunnTest(salrange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
testres_ph
testres_ph$res[testres_ph$res$P.adj < 0.05,]

##plots
# vs temp range
testres_ph <- dunnTest(temprange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(19, 21)
epimesotemp <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Family != "",], aes(x = Family, y = temprange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab(expression(Range~(degree*C))) + 
  xlab(NULL) + 
  ggtitle("Temperature")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 23, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesotemp

testres_ph <- dunnTest(fluorrange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(2.45)
epimesofluor <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Family != "",], aes(x = Family, y = fluorrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(axis.title.y = element_markdown())+ 
  xlab(NULL) + 
  theme(axis.title.y = element_markdown(),
        plot.title = element_markdown())+ 
  ylab("Range (\U003BCg L<sup>-1</sup>)")+
  ggtitle("Chl-a")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.8, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesofluor

testres_ph <- dunnTest(oxyrange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
nsamples_posthoc$ypos <- c(300)
epimesooxy <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Family != "",], aes(x = Family, y = oxyrange)) + 
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylab(expression(Range~(µmol~kg^-1))) + 
  xlab(NULL) + 
  ggtitle("Oxygen")+ 
  stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 325, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 
epimesooxy

testres_ph <- dunnTest(salrange ~ Family,
                       data=together_taxtable_atleast10[together_taxtable_atleast10$Family != "",],
                       method="bonferroni")
nsamples_posthoc <- testres_ph$res[testres_ph$res$P.adj < 0.05,]
nsamples_posthoc$group1 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 1)
nsamples_posthoc$group2 <- sapply(strsplit(nsamples_posthoc$Comparison, " - "), '[', 2)
#nsamples_posthoc$P.adj.sig <- NA
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.05] <- "*"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.01] <- "**"
nsamples_posthoc$P.adj.sig[nsamples_posthoc$P.adj < 0.001] <- "***"
#nsamples_posthoc$ypos <- c(300)
epimesosal <- ggplot(together_taxtable_atleast10[together_taxtable_atleast10$Family != "",], aes(x = Family, y = salrange)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.4, size = 0.5) +
  geom_violin(alpha=0.3) +
  stat_summary(fun = "mean",
               geom = "point",
               color = "black")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylab("Range") +
  xlab(NULL) +
  ggtitle("Salinity")+
  # stat_pvalue_manual(data = nsamples_posthoc, label = "P.adj.sig", y.position = "ypos", tip.length = 0.01) +
  stat_compare_means(method = "kruskal.test", label.y = 2.1, 
                     label.x.npc = "center",
                     label = "p.signif",
                     symnum.args = list(cutpoints = c(0, 0.001, 0.01, 0.05, 1), symbols = c("***", "**", "*", "ns"))) 



plots_copes <- ggarrange(epimesotemp + ylim(0,25), epimesofluor + ylim(0,3), epimesooxy + ylim(0,350), ncol = 3, nrow = 1, align = "hv", labels = "auto")
plots_copes_secondrow <- ggarrange(epimesotemp + ylim(0,25), epimesofluor + ylim(0,3), epimesooxy + ylim(0,350), ncol = 3, nrow = 1, align = "hv", labels = c("d", "e", "f"))

plots <- ggarrange(plots_classes, plots_copes_secondrow, ncol = 1, nrow = 2)



pdf(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/classes+copefamilies_taxa_observedenviroranges_sig.pdf", height =6, width = 6)
plots
dev.off()


jpeg(file = "~/Documents/Chapter2/manuscript_analysis/R/Plots_For_Publication/classes+copefamilies_taxa_observedenviroranges_sig.jpeg", height =6, width = 6, unit = "in", quality = 100, res = 300 )
plots
dev.off()
```

